\documentclass{lucs-art}
\usepackage{xspace}
\newcommand{\tested}{TeStED\xspace}
\newcommand{\ltoe}{LEARN{\kern 1pt}2\emph{Engage}\xspace}
\usepackage[compact]{titlesec}
\usepackage{enumitem}
%\setlist{itemsep=-2pt}

\title{\ltoe: Immediate help}
\author{Iain Phillips\and Dominik Freydenberger}
\date{March 2020}
\begin{document}
\maketitle

\section{LEARN2Engage}\label{learn2engage}

Dominik Freydenberger and Iain Phillips (Computer Science) have a
science TESTED project (called \ltoe) to build a picture of student
engagement. The intention is for students to be better informed about
how well they are engaging with the teaching delivery. Development was
going to take place over the summer in time for a deployment for testing
in Semester 1 20/21 academic year. However, until then, here are a few
things you can do in the meantime to measure how your students are
engaging with your classes.

\section{Simple Guides}\label{simple-guides}

\subsection{Activity usage of a single
resource}\label{activity-usage-of-a-single-resource}

\begin{itemize}
\item
  Module
  page$\rightarrow$Adminsitration$\rightarrow$Reports$\rightarrow$Logs
\item
  Pick and activity from the menu and View from the next menu
\item
  tells you which students have viewed that item
\end{itemize}

\subsection{Full report on a student}\label{full-report-on-a-student}

\begin{itemize}
\item
  Module Page$\rightarrow$Administration$\rightarrow$Users$\rightarrow$Enrolled Users
\item
  Pick a user then click ``Complete Report'': Tells you how many times a
  user has looked at an activity and the time of the most recent access
\item
  Pick a user and then click ``All logs'': Shows logs for this user and
  a bar chart that represents that user's activity over time.
\end{itemize}

\subsection{User usage of activities}\label{user-usage-of-activities}

\begin{itemize}
\item
  Module Page-\textgreater{} Administration -\textgreater{} Reports
  -\textgreater{} Activity report
\item
  list all activities and how many users (not students) have accessed it
\end{itemize}

\subsection{Richer report on user
usage}\label{richer-report-on-user-usage}

\begin{itemize}
\item
  Module Page$\rightarrow$Administration$\rightarrow$Course
  participation
\item
  select an activity and a user group (e.g. students)
\item
  Displays a list of all users and how often they have accessed the
  activity. The list can be sorted by the number of accesses or you can
  pick a particular student.
\item
  Clicking on the student name allows you to get to the per student
  reports.
\end{itemize}

\section{Notes}\label{notes}

It reports on an activity. So if the activity changes, e.g. text in a
label or file in a download, then these are all collected together. This
might affect how you map your resources to activities.
\end{document}